Abstract

### 2024-09-16 output/Main_text.Rmd
Add extra padding around table 1 and figure 1
Update printed keywords to attribute values

*Keywords:* Multidimensional IRT, 2-Parameter Logistic model,
multidimensional item discrimination, multidimensional item difficulty,
item vector representation, test space

>>>>

*Keywords:* Multidimensional 2-Parameter Logistic model,
multidimensional item discrimination, multidimensional item difficulty,
item vector representation, test space
